\thesistitle

### 2019-08-23 sections/clonerefactor.tex
CloneRef

\subsubsection{Impact on maintainability metrics} \label{sec:metrics}
We measure the impact on maintainability metrics of the refactored source code for each clone class that is refactored. These metrics are derived from Heitlager et al. \cite{heitlager2007practical}. This paper defines a set of metrics to measure the maintainability of a system. For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.

@@

\subsection{Saving refactored code}
CloneRefactor features several ``Refactoring Strategies'', that indicate how and where refactored code will be saved. These are as follows:
\begin{itemize}
  \item \textbf{Do not refactor}: CloneRefactor does not apply refactorings at all, it only reports found clones.
  \item \textbf{Simulate}: CloneRefactor only applies the refactorings to its internal AST structure and calculates the results of applying these refactorings. It does not modify/copy the codebase on disk.
  \item \textbf{Replace}: CloneRefactor replaces the source code with the refactored source code.
  \item \textbf{Copy Only Changes}: CloneRefactor writes only the changed files to a new location.
  \item \textbf{Copy All}: CloneRefactor copies the entire project to a new location and applies the refactorings there. This makes sure the original project stays unmodified, while also having a snapshot of the refactored project.
  \item \textbf{Git Replace}: CloneRefactor creates a branch on the git VCS, or initializes a git repository if it is not available. For every clone class refactored, CloneRefactor creates a commit in the git repository.
  \item \textbf{Git Copy}: CloneRefactor copies the entire project to a new location. CloneRefactor then performs the same procedure as for ``Git Replace'', except now at the new location so the original project remains unmodified.
\end{itemize}
These ``Refactoring Strategies'' can be used to get more data regarding the transformations applied by CloneRefactor. In our experiments, we only make use of the ``Simulate'' ``Refactoring Strategy''.

>>>>

\subsubsection{Impact on maintainability metrics} \label{sec:metrics}
We measure the impact on maintainability metrics of the refactored source code for each clone class that is refactored. These metrics are derived from Heitlager et al. \cite{heitlager2007practical}. This paper defines a set of metrics to measure the maintainability of a system. For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system as a whole.

@@

%\subsection{Saving refactored code}
%CloneRefactor features several ``Refactoring Strategies'', that indicate how and where refactored code will be saved. These are as follows:
%\begin{itemize}
%  \item \textbf{Do not refactor}: CloneRefactor does not apply refactorings at all, it only reports found clones.
%  \item \textbf{Simulate}: CloneRefactor only applies the refactorings to its internal AST structure and calculates the results of applying these refactorings. It does not modify/copy the codebase on disk.
%  \item \textbf{Replace}: CloneRefactor replaces the source code with the refactored source code.
%  \item \textbf{Copy Only Changes}: CloneRefactor writes only the changed files to a new location.
%  \item \textbf{Copy All}: CloneRefactor copies the entire project to a new location and applies the refactorings there. This makes sure the original project stays unmodified, while also having a snapshot of the refactored project.
%  \item \textbf{Git Replace}: CloneRefactor creates a branch on the git VCS, or initializes a git repository if it is not available. For every clone class refactored, CloneRefactor creates a commit in the git repository.
%  \item \textbf{Git Copy}: CloneRefactor copies the entire project to a new location. CloneRefactor then performs the same procedure as for ``Git Replace'', except now at the new location so the original project remains unmodified.
%\end{itemize}
%These ``Refactoring Strategies'' can be used to get more data regarding the transformations applied by CloneRefactor. In our experiments, we only make use of the ``Simulate'' ``Refactoring Strategy''.
